%-------------------------
% Resume in Latex
% Author : Jake Rothstein
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage{lmodern}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Jake Rothstein} \\ \vspace{1pt}
    \small 415-969-0949 $|$ \href{mailto:jake.b.rothstein@gmail.com}{\underline{jake.b.rothstein@gmail.com}} $|$ 
    \href{https://linkedin.com/in/j-rothstein}{\underline{linkedin.com/in/j-rothstein}} $|$
    \href{https://github.com/jakerothstein}{\underline{github.com/jakerothstein}} $|$
    US Citizen
\end{center}

%-----------Education-----------

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading{Georgia Institute of Technology}{Atlanta, GA}
    {B.S. Computer Science, GPA: 3.9}{(Expected) May 2027}
    \resumeItemListStart
      \resumeItem{Threads: System Architecture \& Cyber Security; Member, GreyHat Cyber Security Club}
      \resumeItem{Courses: Human Dimension of Cybersecurity, Systems \& Networks, Data Structures \& Algorithms, Design \& Analysis of Algorithms, Computer Organization \& Programming, Objects \& Design, Discrete Math}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
%-----------Experence-----------

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading{The Home Depot}{San Francisco, CA (Remote) / Atlanta, GA}
    {Software Engineer Intern}{Summer 2025}
    \resumeItemListStart
      \resumeItem{Partnered with Product, Design, and Engineering teams to re-architect and enhance event software for 100+ annual events used by 5000+ associates.}
      \resumeItem{Developed web app with Slack integrations using Java Spring Boot and React, deployed on Google Cloud Kubernetes with automated GitHub CI/CD pipelines.}
    \resumeItemListEnd

    \resumeSubheading{GT Financial Services Innovation Lab}{Atlanta, GA}
    {Undergraduate NLP Researcher}{2025 -- Present}
    \resumeItemListStart
      \resumeItem{Designed 150+ annotated credit card agreement questions using numerical reasoning techniques (CoT and PoT) for NLP model training and evaluation.}
      \resumeItem{Built statistical and visual reports comparing industry and cyber risk over time from SEC 10-K filings using tokenization and semantic analysis.}
      \resumeItem{Part of NLP Vertically Integrated Projects (VIP) program under Dr. Sudheer Chava; publication expected 2026.}
    \resumeItemListEnd

    \resumeSubheading{Computacenter}{Remote}
    {Software Engineer Intern}{2022 -- 2023}
    \resumeItemListStart
      \resumeItem{Created a Slack app enabling admins to on/offboard 5K+ employees across systems like ServiceNow, Opsgenie, PRTG, and Slack using FastAPI.}
      \resumeItem{Developed hardware error monitoring tool interfacing with NocoDB, scaled to 50+ customers.}
    \resumeItemListEnd

    \resumeSubheading{Neucargo}{San Francisco, CA}
    {Co-Founder}{Summer 2022}
    \resumeItemListStart
      \resumeItem{Developed Smartsheet integration to automate tracking of UPS, FedEx, and MACH1 shipment statuses.}
    \resumeItemListEnd

    \resumeSubheading{The Burlingame B}{Burlingame, CA}
    {Managing Editor, Head Photographer}{2021 -- 2024}
    \resumeItemListStart
      \resumeItem{Trained 30-person journalism staff in journalistic writing, photography, and digital media.}
      \resumeItem{Automated daily assignments and deadline reminders, ensuring no gaps in coverage.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd
%-----------Projects-----------

\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading{\textbf{PDF Malware Detector (Millennium Capital)} $|$ \emph{Python, SVM, ML}}{\textit{Spring 2025}}
    \resumeItemListStart
      \resumeItem{Built SVM-based malware detector using 2022 dataset; extracted structural features and scaled data; benchmarked against logistic regression and Random Forest with ~88\% accuracy. Presented project at Millennium NYC office.}
    \resumeItemListEnd
    \vspace{-4pt}

    \resumeProjectHeading{\textbf{LeadDog AI (Startup)} $|$ \emph{Python, Web Scraping, API}}{\textit{Summer 2024}}
    \resumeItemListStart
      \resumeItem{AI lead generation software identifying employees for targeted sales campaigns; bypassed rate limits of public/private APIs using various techniques.}
    \resumeItemListEnd
    \vspace{-4pt}

    \resumeProjectHeading{\textbf{PlantX (Columbia AI Seminar)} $|$ \emph{AI Search, Python}}{\textit{Summer 2023}}
    \resumeItemListStart
      \resumeItem{Built AI search algorithm to predict plant disease with ~80\% accuracy.}
    \resumeItemListEnd
    \vspace{-4pt}

    \resumeProjectHeading{\textbf{StudyBot (Personal)} $|$ \emph{Python, AWS EC2, Discord API}}{\textit{Fall 2020}}
    \resumeItemListStart
      \resumeItem{Developed multiplayer Discord trivia game using Quizlet sets, deployed to 100+ discord servers.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, Go, JavaScript, C/C++, SQL, HTML/CSS, Assembly, Markdown, PostgreSQL, TypeScript} \\
     \textbf{Frameworks}{: Java Spring Boot, Flask, ReactJS, Django, Material-UI, CSS, Kubernetes, FastAPI} \\
     \textbf{Developer Tools}{: Git, Docker, VSCode, IntelliJ, Burp Suite, PyCharm, GoLand} \\
     \textbf{Libraries}{: Pandas, NumPy, PyTorch, TensorFlow, OpenCV, BeautifulSoup} \\
     \textbf{Other Skills}{: AWS, GCP, Agile, Linux, Adobe (PS, LR, Premiere), Jira, Ghidra, CI/CD pipelines, NLP}
    }}
 \end{itemize}
\end{document}
